---
title: "Recommendations for QANTAS: USA airport infrastucture, and a domestic aircraft storage facility"
subtitle: ETC5512 Assignment 1, Master of Business Analytics
author: Peizhao Chen, 31377203, pche0072@student.monash.edu 
date: 'April 16, 2021'
output: 
  html_document:
    css: monashreport.css
    includes:
      before_body: header.html
---

```{r}
install.packages("naniar")
install.packages("do")
install.packages("scatterplot3d")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache=TRUE, 
                      messages=FALSE, 
                      warning=FALSE)
library(tidyverse)
library(ggmap)
library(ggplot2)
library(knitr)
library(naniar)
library(scatterplot3d)
```
 
## Task 1

```{r}

setwd("C:/Users/Administrator/Desktop/Monash BA/ETC5512/Assignment/ETC-5512")
Flight_data <- read.csv("data/1067097428_T_ONTIME_REPORTING.csv")

```

```{r}
LAX_DFW_ORIGIN_Data <- Flight_data %>%
  dplyr::select(c(`YEAR`:`ARR_DELAY`)) %>%
         filter(ORIGIN %in% c("LAX","DFW"))

LAX_DFW_ORIGIN_Data[is.na(LAX_DFW_ORIGIN_Data)]<-0
```

```{r}

LAX_DFW_DEST_Data <- Flight_data %>%
  dplyr::select(c(`YEAR`:`ARR_DELAY`)) %>%
         filter(DEST %in% c("LAX","DFW"))

LAX_DFW_DEST_Data[is.na(LAX_DFW_DEST_Data)]<-0                
```

```{r}


SUM_OF_DELAY <- LAX_DFW_ORIGIN_Data %>%
  dplyr::select("ORIGIN",
                "DEP_DELAY",
                "ARR_DELAY")%>%
         pivot_longer(cols = -"ORIGIN",
                      names_to = "DELAY",
                      values_to = "TIME") %>%
         group_by(ORIGIN,DELAY) %>%
         summarise(SUM_OF_DELAY= sum(TIME))

knitr::kable(SUM_OF_DELAY, booktabs = TRUE,
  caption = 'DELAY ')         
    
```

```{r}

SUM_OF_DELAY_ORIGIN <- LAX_DFW_ORIGIN_Data %>%
  dplyr::select("ORIGIN",
                "DEP_DELAY",
                "ARR_DELAY")%>%
         pivot_longer(cols = -"ORIGIN",
                      names_to = "DELAY",
                      values_to = "TIME") %>%
         group_by(ORIGIN,DELAY) %>%
         summarise(SUM_OF_DELAY= sum(TIME))

ggplot(SUM_OF_DELAY_ORIGIN,aes(x=DELAY,
                        y=SUM_OF_DELAY))+
  geom_col()+
  facet_grid(~ORIGIN)+
  ggtitle("Figure 1:Total delay time")
 
```

From the figure and table above show that when LAX and DFW are served as origin,they have apparently different mode.DWF has larger sum of delay both in arr and dep,and sum of delay are positive number which means the number of delay flights is larger than on-time flight.LAX also has larger number of dep delay flights compare with on-time flight,but its ARR delay time is negative that means pilots may drive faster and arrive at destination earlier.

```{r}

SUM_OF_DELAY_DEST <-LAX_DFW_DEST_Data %>%
  dplyr::select("DEST",
                "DEP_DELAY",
                "ARR_DELAY")%>%
         pivot_longer(cols = -"DEST",
                      names_to = "DELAY",
                      values_to = "TIME") %>%
         group_by(DEST,DELAY) %>%
         summarise(SUM_OF_DELAY= sum(TIME))

 ggplot(SUM_OF_DELAY_DEST,aes(x=DELAY,
                        y=SUM_OF_DELAY))+
  geom_col()+
  facet_grid(~DEST)+
  ggtitle("Figure 2:Total delay time") 
```
Similar to the figure 1 ,but in figure 2.The sum of ARR time is even negatively larger when lax served as destination,which means flights are operated more efficient.

```{r}
WEEKLY_Mode_of_Delay_Origin <-LAX_DFW_ORIGIN_Data %>%
  dplyr::select("ORIGIN",
                "DAY_OF_WEEK",
                "DEP_DELAY",
                "ARR_DELAY")%>%
         pivot_longer(cols =  'DEP_DELAY':'ARR_DELAY',
                      names_to = "DELAY",
                      values_to = "TIME") %>%
         group_by(ORIGIN,DELAY,DAY_OF_WEEK) %>%
         summarise(SUM_OF_DELAY= sum(TIME))


ggplot(WEEKLY_Mode_of_Delay_Origin,aes(x= DAY_OF_WEEK,
                                y= SUM_OF_DELAY,
                                fill= DELAY))+
    geom_col()+ 
    facet_grid(~ ORIGIN)+
    scale_fill_brewer(palette = "Dark2")+
    ggtitle("Figure 3:WEEKLY_Mode_of_Delay_Origin")
   
    
```

```{r}
WEEKLY_Mode_of_Delay_DEST <-LAX_DFW_DEST_Data %>%
  dplyr::select("DEST",
                "DAY_OF_WEEK",
                "DEP_DELAY",
                "ARR_DELAY")%>%
         pivot_longer(cols =  'DEP_DELAY':'ARR_DELAY',
                      names_to = "DELAY",
                      values_to = "TIME") %>%
         group_by(DEST,DELAY,DAY_OF_WEEK) %>%
         summarise(SUM_OF_DELAY= sum(TIME))


ggplot(WEEKLY_Mode_of_Delay_DEST,aes(x= DAY_OF_WEEK,
                                y= SUM_OF_DELAY,
                                fill= DELAY))+
    geom_col()+ 
    facet_grid(~ DEST)+
    scale_fill_brewer(palette = "Dark2")+
    ggtitle("Figure 4:WEEKLY_Mode_of_Delay_Origin")
```
From the information provided by Figure 3 and Figure 4,flight delay tend to focus on Monday,Thursday and Friday,and on-time flights  mainly occured in Tuesday and Wednesday.Interestingly,LAX airport has significant different in terms of on-time flights in Monday and Sunday,especially when LAX used as origin,since it have more earlier arrival flight in most days of a week. 

# Summary for the comparision of two airports

Briefly,LAX airport has relatively high efficiency in terms of operation which can be demonstrate through amount of delay by given table and figure.Maybe DFW can try to resolve this situation through improve their operational performence in Monday,Thursday and Friday.

## Task 2

```{r}

setwd("C:/Users/Administrator/Desktop/Monash BA/ETC5512/Assignment/ETC-5512")
Animal_Data <- read.csv("data/records-2021-04-15-2.csv")

```

```{r}
Location_data <- Animal_Data %>% 
dplyr::filter(locality %in% c("Tullamarine",
                              "Bendigo"))%>%
       select("eventDate",
              "locality",
              "decimalLatitude",
              "decimalLongitude",
              "geodeticDatum",
              "species",
              "individualCount",
              "eventTime")
       
```

```{r}

Number_OF_Occurances <-Location_data %>%
dplyr::filter(locality %in% c("Tullamarine",
                              "Bendigo"))%>%
       select("eventDate",
              "locality",
              "decimalLatitude",
              "decimalLongitude",
              "geodeticDatum",
              "species")%>%
       group_by(locality) %>%
       count(species,name = "occurance")

knitr::kable(Number_OF_Occurances,
  caption = 'Number of Occurances')

```

```{r}
Number_OF_Occurances_Illustration <-Location_data %>%
dplyr::filter(locality %in% c("Tullamarine",
                              "Bendigo"))%>%
       select("eventDate",
              "locality",
              "decimalLatitude",
              "decimalLongitude",
              "geodeticDatum",
              "species")%>%
       group_by(locality) %>%
       count(species,name = "occurance")

ggplot(Number_OF_Occurances, aes(x= locality,
                                 y= occurance))+
  geom_col()+
  facet_grid(~ species)+
  ggtitle("Number OF Occurances")
```

From the given table and figure, these two locations,Tullamarine and Bendigo are habitats for
Anthochaera phrygia and Perameles gunnii respectively.They live in different places and the size of the herds are remain in a really smalll,around 1 to 2.Apparently,the number of species activiites has be recorded in Bendigo is twice higher than which in Tullamarine.

```{r}

Time_of_Occurance_Illustration <- Location_data %>%
  dplyr::select("eventDate",
                "species",
                "decimalLatitude",
                "decimalLongitude") %>%
          mutate(Accurate_Location = str_c(decimalLatitude,decimalLongitude,sep = ",")) 

ggplot(Time_of_Occurance_Illustration,aes(x =eventDate,
                                          y =Accurate_Location))+
  geom_line(position=position_dodge(0.2))+
  geom_point(size=4, shape=20)+
  facet_grid(~ species)+
  theme_dark()+
  ggtitle("Time of Occurance Illustration")

```

In the figure above,the activities of Anthochaera phrygia was mainly happend before 2000 ,this indicate that they might migrate to other habitats rather than original location (-36.77,144.28) and (-36.75,144.27).by comparision,the activities of Perameles gunnii  was happend after 2000 and focus in location(-37.6311,144.8486).Given that the herd of Perameles gunnii do not likely to move,so they might still live in this area.

```{r}
map=get_map(location='Vectoria',maptype='roadmap',zoom=12)
register_google()
```

————————————————



## Resources

 Winnard, A. L. & Coulson, G. (2008). "Sixteen years of Eastern Barred Bandicoot Perameles gunnii reintroductions in Victoria: a review". Pacific Conservation Biology. 14: 34. doi:10.1071/PC080034.

R Core Team (2021). R: A language and environment for
statistical computing. R Foundation for Statistical
Computing, Vienna, Austria. URL
https://www.R-project.org/.

## Supplementary information

Any material that you think is important to include, but does not fit well in the main report can go here. The marker will likely not look at this section. So choose carefully, anything important needs to be in sections 1 (Task 1) and 2 (Task 2).
