---
title: "Recommendations for QANTAS: USA airport infrastucture, and a domestic aircraft storage facility"
subtitle: ETC5512 Assignment 1, Master of Business Analytics
author: Peizhao Chen, 31377203, pche0072@student.monash.edu 
date: 'April 16, 2021'
output: 
  html_document:
    css: monashreport.css
    includes:
      before_body: header.html
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      cache=TRUE, 
                      messages=FALSE, 
                      warning=FALSE)
library(tidyverse)
```

```{r}

```



## Task 2

Your comparison of domestic storage sites goes here

## Resources

Cite your data sources, and software used here

R Core Team (2021). R: A language and environment for
statistical computing. R Foundation for Statistical
Computing, Vienna, Austria. URL
https://www.R-project.org/.

## Supplementary information

Any material that you think is important to include, but does not fit well in the main report can go here. The marker will likely not look at this section. So choose carefully, anything important needs to be in sections 1 (Task 1) and 2 (Task 2).
